---
title: "READ ME AND CODE BOOK for Getting and Cleaning Data Final Project"
author: "Jay Vera"
date: "2024-09-09"
output: html_document
---
READ ME

Peer-graded Assignment: Getting and Cleaning Data Course Project
This repository is a Jay Vera submission for Getting and Cleaning Data course project. It has the instructions on how to run analysis on Human Activity recognition dataset.

Dataset
Human Activity Recognition Using Smartphones
http://archive.ics.uci.edu/ml/datasets/Human+Activity+Recognition+Using+Smartphones

Files
CodeBook.md a code book that describes the variables, the data, and any transformations or work that I performed to clean up the data

run_analysis.R performs the data preparation and then followed by the 5 steps required as described in the course project’s definition:

1)Merges the training and the test sets to create one data set.
2)Extracts only the measurements on the mean and standard deviation for each measurement.
3)Uses descriptive activity names to name the activities in the data set
4)Appropriately labels the data set with descriptive variable names.
5)From the data set in step 4, creates a second, independent tidy data set with the average of each variable for each activity and each subject.
6)FinalData.txt is the exported final data after going through all the sequences described above.


CODE BOOK

The run_analysis.R script performs the data preparation and then followed by the 5 steps required as described in the course project’s definition.

1. Download the dataset
1.1. Dataset downloaded and extracted under the folder called UCI HAR Dataset

2. Assign each data to variables

2.1. Features (561 rows, 2 columns)
```{r setup, include=FALSE}
features <- features.txt
```
The features selected for this database come from the accelerometer and gyroscope 3-axial raw signals tAcc-XYZ and tGyro-XYZ.

2.2. Activities (6 rows, 2 columns)
```{r setup, include=FALSE}
activities <- activity_labels.txt
```
List of activities performed when the corresponding measurements were taken and its codes (labels)

2.3 Subject Test (2947 rows, 1 column)
```{r setup, include=FALSE}
subject_test <- test/subject_test.txt
```
Test data of 9/30 volunteer test subjects being observed

2.4 X test (2947 rows, 561 columns)
```{r setup, include=FALSE}
x_test <- test/X_test.txt
```
Recorded features test data

2.5 Y test (2947 rows, 1 columns)
```{r setup, include=FALSE}
y_test <- test/y_test.txt
```
Test data of activities’code labels

2.6 Subject train (7352 rows, 1 column)
```{r setup, include=FALSE}
subject_train <- test/subject_train.txt
```
Train data of 21/30 volunteer subjects being observed

2.7 X train (7352 rows, 561 column)
```{r setup, include=FALSE}
x_train <- test/X_train.txt
```
Recorded features train data

2.8 Y train (7352 rows, 1 columns)
```{r setup, include=FALSE}
y_train <- test/y_train.txt
```
Train data of activities’code labels

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

